Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-25 Cover_letter_JPM.tex
Answer 2-5 done (2021/06/25)

% mark in blue or red
\usepackage{xcolor}

\newenvironment{MyColorPar}[1]{%
    \leavevmode\color{#1}\ignorespaces%
}{%
}%

@@

We appreciate the reviewer for the critical comments.
 %=> includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
Since we have tried to integrate multiple genes in survival analysis, a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
Searching about the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression. %The dependent variables are the survival data.
%Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
%Least Absolute Shrinkage and Selection Operation (LASSO):
Branders and his colleagues\cite{Branders2014} have suggested that regularization of regression model should be applied on analysis of the high-dimensional data, i.e. twenty thousands of features (genes) and only hundreds of sample size.
The $L_{1}$-regularized path algorithm by Least Absolute Shrinkage and Selection Operation (LASSO) regression could perform feature selection (a subset of gene).
LASSO is suitable at picking up a small signal (gene signature) through lots of noise (twenty thousands of protein-coding genes).
% R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html
Our approach is to build a logistic regression model for the prediction of patient's survival.
% over-fitting causes problem
% During fitting of logistic model, 
Beside feature selection,
it is also necessary to add that small amount of bias (lambda, $\lambda$) for getting a significant drop in the variance to prevent over-fitting of the model.
$\lambda$ could control the amount of bias dealing with over-fitting.
%(over-fitting is called high-variance)
In such a case, over-fitted model will only perfectly match every individual cases, and has higher variability to predict what it never see.
Over-fitting will limit usefulness of the model in it's generalization, and could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
% feature selection by lasso (L1 regularization)
% LASSO, shrinkage coefficients to zero, for selection the features
% perhaps the simplest and 
Cross-validation error is calculated to find the optimal value of $\lambda$.
%Cross-validation is most widely used method for select one of models at specific regularization rate (i.e. lambda, \lambda) during the model fitting.
% k-fold Cross-validation
As the coefficients of logistic regression are reduced to zero by LASSO, %the useless features (genes) associated with those coefficients will be omitted.
the important features that contribute much to the model will be selected under that optimal value of $\lambda$.

% multinomial
%RLassoCox\\
We have utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) for training the Cox proportional hazard regression and logistic regression models in gene expression analysis to identify a group of genes that contribute to survival outcome of HNSCC patient. 
%and gene interaction networks (The KEGG network\cite{Simon2011}).
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
% based on gene expression profiles,
%The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
The RLassoCox make use of both Cox and LASSO logistic regression for gene-expression based survival analysis.
The model training has been performed under 10-fold cross-validation.
% medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d

@@

% **** [2021/06/22] by Bayes_survival.R
The results shows
% k-fold Cross-validation
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
#Calculating Cox p-value...Done [2021/06/22] 19:42
#Performing directed random walk...Done
#Performing cv.glmnet...Done
#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
the selected features (62 genes) are selected by their (non-zero) coefficients. 
%cv.mod.candidate has 62 genes 
However, they are performed poor either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\

\begin{figure}[!tbp]
%     % two PDF side by side \usepackage{subcaption}
  \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf}
        \caption{TCGA HNSCC cohort}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
       \includegraphics[width=\textwidth]{Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf} 
       \caption{GSE65858 HNSCC cohort}
  \end{subfigure}
  \caption{side by side}
  \label{fig:Bayes62}
\end{figure}

% accuracy for the classification in case-control study (or ROC, AUC)
% **** C-index, concordance index for survival data (with censoring)
the Harrell concordance index (C-index) (1996) is the standard performance metric for model assessment in survival analysis with censored data.
%The predictive performances are computed in terms of C-index for the survival prediction.

% Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
the left vertical line in the plot shows us where the cross-validation error curve hits its minimum. 
The right vertical line shows us the most regularized model with the cross-validation error within 1 standard deviation of the minimum.
% in lambda 1se
%cv.mod$glmnetRes$lambda.1se
the most regularized model with cross-validation error within 1 standard deviation of the minimum.
It selects 14 genes,
according to the \textit{P} value, 4 gene signature: HK1, EZR, RRAGA, and DUSP16.

% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
Finally, we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).

However, # 4 gene signature: #### 
# "EZR" has \textit{P} value $>0.05$

Conclusion, we might build a Lasso regression model with L1 regularization to maximize the use of continuous gene expression values (without a cutoff).
The gene signature integrating multiple genes is also a good approach for biomarker discovery.

\begin{figure}
%    \centering
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=8cm]{rplot_KMplot_HK1.pdf}
    \caption{Kaplan-Meier plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
    \caption{Volcano plot}
  \end{subfigure}

  \caption{(a) OS in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16; (b) Those genes have not significant survival impact if calculated individually (EZR is not shown on volcano plot due to it's \textit{P} value $>0.05$)}
    \label{fig:signature4}
\end{figure}

>>>>

% mark in blue or red
\usepackage{xcolor}
%\usepackage[table,xcdraw]{xcolor}
\newenvironment{MyColorPar}[1]{%
    \leavevmode\color{#1}\ignorespaces%
}{%
}%

@@

We appreciate the reviewer for the critical comments.
Since we have tried to integrate multiple genes in survival analysis, a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
Searching about the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression. %The dependent variables are the survival data.
%Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
%Least Absolute Shrinkage and Selection Operation (LASSO):
Branders and his colleagues\cite{Branders2014} have suggested that regularization of regression model should be applied on analysis of the high-dimensional data, i.e. twenty thousands of features (genes) and only hundreds of sample size.
The $L_{1}$-regularized path algorithm by Least Absolute Shrinkage and Selection Operation (LASSO) regression could perform feature selection (a subset of gene).
LASSO is suitable at picking up a small signal (gene signature) through lots of noise (twenty thousands of protein-coding genes).
% R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html
Our approach is to build a logistic regression model for the prediction of patient's survival.
% over-fitting causes problem
% During fitting of logistic model, 
Beside feature selection,
it is also necessary to add that small amount of bias (lambda, $\lambda$) for getting a significant drop in the variance to prevent over-fitting of the model.
$\lambda$ could control the amount of bias dealing with over-fitting.
%(over-fitting is called high-variance)
In such a case, over-fitted model will only perfectly match every individual cases, and has higher variability to predict what it never see.
Over-fitting will limit usefulness of the model in it's generalization, and could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
% feature selection by lasso (L1 regularization)
% LASSO, shrinkage coefficients to zero, for selection the features
% perhaps the simplest and 
Cross-validation error is calculated to find the optimal value of $\lambda$.
%Cross-validation is most widely used method for select one of models at specific regularization rate (i.e. lambda, \lambda) during the model fitting.
% k-fold Cross-validation
As the coefficients of logistic regression are reduced to zero by LASSO, %the useless features (genes) associated with those coefficients will be omitted.
the important features that contribute much to the model will be selected under that optimal value of $\lambda$.

% multinomial
%RLassoCox\\
We have utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) for training the Cox proportional hazard regression and logistic regression models in gene expression analysis to identify a group of genes that contribute to survival outcome of HNSCC patient. 
% RLassoCox includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
% gene interaction networks (The KEGG network\cite{Simon2011}).
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
% based on gene expression profiles,
%The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
The RLassoCox make use of both Cox and LASSO logistic regression for gene-expression based survival analysis.
The model training has been performed under 10-fold cross-validation.
% medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d

@@

% **** [2021/06/22] by Bayes_survival.R
% k-fold Cross-validation
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
%#Calculating Cox p-value...Done [2021/06/22] 19:42
%#Performing directed random walk...Done
%#Performing cv.glmnet...Done
%#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
%cv.mod.candidate has 62 genes 
The results shows the selected features (62 genes) distributing on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}).

\begin{figure}[!tbp]
%     % two PDF side by side \usepackage{subcaption}
  \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf}
        \caption{TCGA HNSCC cohort}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
       \includegraphics[width=\textwidth]{Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf} 
       \caption{GSE65858 HNSCC cohort}
  \end{subfigure}
  \caption{The 62 genes (listed on the right) have been discovered by LASSO regression in (a) TCGA HNSCC and (b) GSE65858 HNSCC cohort. \textcolor{red}{Red}-square marked genes are our 3 candidates.}
  \label{fig:Bayes62}
\end{figure}

% C-index = 0.68 in this model fitting
%accuracy for the classification in case-control study (or ROC, AUC)
% **** C-index, concordance index for survival data (with censoring)
%the Harrell concordance index (C-index) (1996) is the standard performance metric for model assessment in survival analysis with censored data.
%The predictive performances are computed in terms of C-index for the survival prediction.

% Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
%the left vertical line in the plot shows us where the cross-validation error curve hits its minimum.
%The final gene signature has been selected, including 4 genes, named HK1, EZR, RRAGA, and DUSP16 .; fentastic4
% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
LASSO calculate the (non-zero) coefficients of features, while the 62 genes hit the minimum of cross-validation error.
% in lambda 1se
%cv.mod$glmnetRes$lambda.1se
We have further limited gene selection (13 out of 62) by the most regularized model under cross-validation error within 1 standard deviation of the minimum.
According to their \textit{P} values (please see Table \ref{tab:signature4}), 
we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1 in volcano plot of TCGA HNSCC.

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
% \usepackage[table,xcdraw]{xcolor}
% {\color[HTML]{FE0000} 0.002}  
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
% Please add the following required packages to your document preamble:

\begin{table}[ht]
\centering
\caption{The most LASSO regularized logistic model under cross-validation. Genes with positive coefficient will increase the patient's risk, while negative reduce it.\\
    (\textcolor{red}{red}-marked logistic \textit{P} value $< 0.05$)}
\label{tab:signature4}
\begin{tabular}{lrr}
\textbf{Gene Symbol} & \textbf{Coefficients} &  \textbf{\textit{P} value} \\ \hline
\textbf{POLR2C}      & 0.870                 & 0.150                              \\
\textbf{EFNB2}       & 0.189                 & 0.521                              \\
\textbf{PLAU}        & -0.189                & 0.408                              \\
\textbf{HK1}         & 1.413                 & \textcolor{red}{0.002}       \\
\textbf{WNT7A}       & 0.211                 & 0.111                              \\
\textbf{HPRT1}       & 0.620                 & 0.113                              \\
\textbf{APP}         & 0.219                 & 0.538                              \\
\textbf{SC5DL}       & 0.262                 & 0.367                              \\
\textbf{EZR}         & 0.973                 & \textcolor{red}{0.017}       \\
\textbf{RRAGA}       & 0.925                 & \textcolor{red}{0.022}       \\
\textbf{S1PR4}       & -0.368                & 0.052                              \\
\textbf{DUSP16}      & -0.745                & \textcolor{red}{0.035}       \\
\textbf{SH3BP2}      & -0.606                & 0.107                             
\end{tabular}
\end{table}

\begin{figure}[ht]
%    \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=6cm]{rplot_KMplot_HK1.pdf}
    \caption{Kaplan-Meier plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
    \caption{Volcano plot}
  \end{subfigure}
%However, # 4 gene signature: #### 
%# "EZR" has \textit{P} value $>0.05$
  \caption{(a) OS in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16 (Kaplan-Meier \textit{P} value = \num{1.31e-6}); (b) Those genes (listed on the rigth side) have not significant hazard ratio (HR) if calculated individually (EZR is not shown on volcano plot due to it's Kaplan-Meier \textit{P} value $>0.05$)}
    \label{fig:signature4}
\end{figure}

In conclusion, we might build a Lasso regression model with LASSO regularization to maximize the use of continuous gene expression values (without the need of a cutoff).
The gene signature integrating multiple genes is also a good approach for biomarker discovery.
However, the resulting candidates could be influenced by proper "gene interaction network" applied for model building.
% gene signature
RLassoCox package works on the basis of gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
RLassoCox utilizes Kyoto Encyclopedia of Genes and Genomes (KEGG) network\cite{Simon2011} as the reference of gene interaction networks, constructed by the R package "iSubpathwayMiner".
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
